---
title       : Project-ddp2014
subtitle    : Project presentation of Unit conversion dynamic UI
author      : Alok Juneja
job         : Presentation made on `r date()`
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : [mathjax]            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Read-And-Delete

1. Edit YAML front matter
2. Write using R Markdown
3. Use an empty line followed by three dashes to separate slides!

--- .class #id 

## Why Unit conversion?

In the present global In our daily life where itemthe field of science, the metric system is used in performing measurements. The metric system is actually easier to use than the English system, as you will see shortly. The metric system uses prefixes to indicate the magnitude of a measured quantity. The prefix itself gives the conversion factor. You should memorize some of the common prefixes, as you will be using them on a regular basis.

--- .class #id 

## Different systems

Length conversion

$^{\circ}\mathrm{C} = (^{\circ}\mathrm{F} - 32)/1.8$ 

--- .class #id 

## R code and shiny (ui.R)

```{r,}
library(shiny)

shinyUI(fluidPage(
  headerPanel("Unit converter"),
  fluidRow(column(10,
    fluidRow(column(4,
      radioButtons("id1", "Choose option",
                   c("Temperature" = "Temperature",
                     "Length" = "Length")),

      # This outputs the dynamic UI component based on the option above
	    uiOutput("ui1"),
      textInput('val1',"Enter the value"),
	    uiOutput("ui2")

    ),
    column(6,
    mainPanel(
        verbatimTextOutput("typ"),
        verbatimTextOutput("ans")
  )))
))))

```

--- .class #id 

## R code and shiny (server.R)

```{r}
library(shiny)

converter <- function(id,from,to,val) {
  switch(id,
  	"Temperature"={
			switch(from,
				"Celsius"={
					switch(to,
						"Celsius" = round(val,digits=6),
						"Fahrenheit" = round((val * 9/5) + 32,digits=6),
						"Kelvin" = round(val + 273.15,digits=6))
				},
				"Fahrenheit"={
					switch(to,
						"Celsius" = round((val - 32 ) * 5/9,digits=6),
						"Fahrenheit" = round(val,digits=6),
						"Kelvin" = round(((val - 32 ) * 5/9) + 273.15,digits=6))
				},
				"Kelvin"={
					switch(to,
					"Celsius" = round(val - 273.15,digits=6),
					"Fahrenheit" = round(((val - 273.15) * 9/5) + 32,digits=6),
					"Kelvin" = round(val,digits=6))
				}
			)
		},
		"Length" = {
			switch(from,
				"Kilometers" = {
					switch(to,
						"Kilometers" = round(val,digits=6),
						"Miles" = round(val * 0.62137,digits=6),
						"Yards" = round(val * 1093.6,digits=6))
				},
				"Miles" = {
					switch(to,
						"Kilometers" = round(val * 1.609344,digits=6),
						"Miles" = round(val,digits=6),
						"Yards" = round(val * 1760,digits=6))
				},
				"Yards" = {
					switch(to,
						"Kilometers" = round(val * 0.00091,digits=6),
						"Miles" = round(val * 0.00056818,digits=6),
						"Yards" = round(val,digits=6))
				}
			)
		}
	)
} 

shinyServer(
  function(input, output) {
	# Depending on input$id1, generate a different conversion units
	# UI component and send it to the client.
  
	output$ui1 <- renderUI({
	  if (is.null(input$id1))
	    return()
    
 		switch(input$id1,
  		"Temperature" = selectInput("from", "From", c("Celsius", "Fahrenheit", "Kelvin")),
  		"Length" = selectInput("from", "From", c("Kilometers", "Miles","Yards")))
  		})

	output$ui2 <- renderUI({
	  if (is.null(input$id1))
	    return()
	  
    switch(input$id1,
  		"Temperature" = selectInput("to", "To", c("Celsius", "Fahrenheit", "Kelvin")),
  		"Length" = selectInput("to", "To", c("Kilometers", "Miles","Yards")))
  		})

  
  output$typ <- renderText({paste("Convert", input$id1 )})	
  output$ans <- renderText({paste(input$val1, input$from, "=",converter(toString(input$id1),toString(input$from),toString(input$to),as.double(input$val1)),input$to)})
  }
)

```